\propertitle

### 2019-07-13 maxNt_v5.tex
update

\pdfoutput=1
%% Author: PGL  Porta Mana
%% Created: 2015-05-01T20:53:34+0200
%% Last-Updated: 2019-07-12T11:25:44+0200
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newif\ifarxiv
\arxivfalse
\ifarxiv\pdfmapfile{+classico.map}\fi
\newif\ifafour
\afourfalse% true = A4, false = A5
\newif\iftypodisclaim % typographical disclaim on the side
\typodisclaimtrue
\newcommand*{\memfontfamily}{zplx}
\newcommand*{\memfontpack}{newpxtext}
\documentclass[\ifafour a4paper,12pt,\else a5paper,10pt,\fi%extrafontsizes,%
onecolumn,oneside,article,%french,italian,german,swedish,latin,
british%
]{memoir}
\newcommand*{\updated}{\today}
\newcommand*{\firstdraft}{4 November 2015}
\newcommand*{\firstpublished}{***}
\newcommand*{\propertitle}{Maximum-entropy distributions for a 
  neuronal network\\ from subnetwork data%\\{\large ***}%
}
\newcommand*{\pdftitle}{\propertitle}
\newcommand*{\headtitle}{Maximum-entropy from sample data}
\newcommand*{\pdfauthor}{P.G.L.  Porta Mana, Y. Roudi, V. Rostami, E. Torre}
\newcommand*{\headauthor}{Porta Mana \etal}
\newcommand*{\reporthead}{}% Report number

@@

\mynote{maybe move this paragraph to the intro?}Present-day technologies
enable the recording of neuronal activity from small brain areas
\mynote{be more specific}. For many animal species, the neurons that are
recorded within the area are not -- and at present cannot be --
specifically chosen from among the rest, owing to several limiting factors;
for example, limitations in the precision with which electrodes are
inserted, or with which neurons are targeted by viruses. In fact, the set
of recorded neurons may even change during very long recordings or across
experimental sessions. We assume that there's a area, comprising a
network of $N$ neurons, from which other sets of neurons had or will have
the same probability of being recorded, even in other experimental
sessions, as the set of $n$ neurons that was actually recorded in this
session. This is our \enquote{full network}.\mynote{how about calling it
  \enquote{the pool}?} The normalized total activity of these $N$ neurons
at $t$ is $\yA_{t}$. The relative frequencies of the various activity
levels during the recording were $(\yFF_{\yA}) \defs \yF$. We don't know the
values $\yA_{t}$ at each $t$, or the frequency distribution $\yF$. We only
know for certain that $\yA_{t} \in \set{0,1/N,\dotsc,(N-1)/N,1}$ and that
$N\yA_{t} \ge n\ya_{t}$ for obvious reasons. For the time being we assume
that we know $N$; in \sect*** we discuss the consequences of our lack of
precise knowledge about this number.

@@

The post-data belief density~\eqref{eq:density_proportional} has a
maximum-entropy distribution as a mode approximation when $\ycs$ is small,
$\yL$ is large, and $\ycs L$ is small: the mode will be the constrained
$\yF$ that minimizes the relative entropy $\ysh(\yF;\yR)$. It should be
noted that a pre-data belief different from the entropic
one~\eqref{eq:entropic_prior} will lead to a different mode approximation.
For example, a Dirichlet density would lead to a maximum-entropy
distribution with \emph{Burg's} entropy \citep{burg1975} instead of
Shannon's \citep{jaynes1986d_r1996,portamana2009}.

@@

\begin{figure}[!p]
\centering
\includegraphics[width=\linewidth]{_scripts/MC_plot1000.pdf}%
\\[3em]%
\includegraphics[width=\linewidth]{_scripts/MC_marginal1000.pdf}%
\caption{***}
\label{fig:MC1000}
\end{figure}
% mctests3.nb
% mcfd_6mom_unif_afssd40st0np_cok_tr_N1000_t50_L50_T0.333333333333333_s60000_a15758.0500981316
\begin{figure}[!p]
\centering
\includegraphics[width=\linewidth]{_scripts/MC_plot5000.pdf}%
\\[3em]%
\includegraphics[width=\linewidth]{_scripts/MC_marginal5000.pdf}%
\caption{***}
\label{fig:MC5000}
\end{figure}
% mctests3.nb
% mcfd_6mom_unif_afssd32s_cok_tr_N5000_t180_L50_T0.333333333333333_s25800_a329212306.071189
The properties of the belief density~\eqref{eq:density_proportional} in the
case of our first data set are shown in \fig~\ref{fig:MC1000} for
$N=1\,000$ and in \fig~\ref{fig:MC5000} for $N=5\,000$. Only the first six
factorial moments were considered as our data, but it turns out that they
are informationally sufficient, leading to practically the same result as
specifying the full frequency distribution for the sample.

>>>>

\pdfoutput=1
%% Author: PGL  Porta Mana
%% Created: 2015-05-01T20:53:34+0200
%% Last-Updated: 2019-07-13T11:35:37+0200
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newif\ifarxiv
\arxivfalse
\ifarxiv\pdfmapfile{+classico.map}\fi
\newif\ifafour
\afourfalse% true = A4, false = A5
\newif\iftypodisclaim % typographical disclaim on the side
\typodisclaimtrue
\newcommand*{\memfontfamily}{zplx}
\newcommand*{\memfontpack}{newpxtext}
\documentclass[\ifafour a4paper,12pt,\else a5paper,10pt,\fi%extrafontsizes,%
onecolumn,oneside,article,%french,italian,german,swedish,latin,
british%
]{memoir}
\newcommand*{\updated}{\today}
\newcommand*{\firstdraft}{4 November 2015}
\newcommand*{\firstpublished}{***}
\newcommand*{\propertitle}{Maximum-entropy distributions for a 
  neuronal network\\ from subnetwork data%\\{\large ***}%
}
\newcommand*{\pdftitle}{\propertitle}
\newcommand*{\headtitle}{Maximum-entropy from sample data}
\newcommand*{\pdfauthor}{P.G.L.  Porta Mana, Y. Roudi, V. Rostami, E. Torre}
\newcommand*{\headauthor}{Porta Mana \etal}
\newcommand*{\reporthead}{}% Report number

@@

\mynote{maybe move this paragraph to the intro?}Present-day technologies
enable the recording of neuronal activity from small brain areas \mynote{be
  more specific}. For many animal species, the neurons that are recorded
within the area are not -- and at present cannot be -- specifically chosen
from among the rest, owing to several limiting factors; for example,
limitations in how precisely electrodes are inserted or neurons are
targeted by viruses. In fact, the set of recorded neurons may even change
during very long recordings or across experimental sessions. We assume that
there's an area, comprising a network of $N$ neurons, from which other sets
of neurons could have been or will be recorded***have the same probability of being recorded, even in
other experimental sessions, as the set of $n$ neurons that was actually
recorded in this session. This is our \enquote{full network}.\mynote{how
  about calling it \enquote{the pool}?} The normalized total activity of
these $N$ neurons at $t$ is $\yA_{t}$. The relative frequencies of the
various activity levels during the recording were $(\yFF_{\yA}) \defs \yF$.
We don't know the values $\yA_{t}$ at each $t$, or the frequency
distribution $\yF$. We only know for certain that
$\yA_{t} \in \set{0,1/N,\dotsc,(N-1)/N,1}$ and that $N\yA_{t} \ge n\ya_{t}$
for obvious reasons. For the time being we assume that we know $N$; in
\sect*** we discuss the consequences of our lack of precise knowledge about
this number.

@@

The post-data belief density~\eqref{eq:density_proportional} has a
maximum-entropy distribution as a mode approximation when $\ycs$ is small,
$\yL$ is large, and $\ycs L$ is small: the mode will be the constrained
$\yF$ that minimizes the relative entropy $\ysh(\yF;\yR)$. It should be
noted that a pre-data belief different from the entropic
one~\eqref{eq:entropic_prior} will lead to a different mode approximation.
For example, a Dirichlet density (which is equivalent
to~\eqref{eq:entropic_prior} with $\yF$ and $\yR$ exchanged) would lead to
a maximum-entropy distribution with \emph{Burg's} entropy \citep{burg1975}
instead of Shannon's \citep{jaynes1986d_r1996,portamana2009}.

@@

\begin{figure}[!p]
\centering
\includegraphics[width=\linewidth]{_scripts/MC_plot1000.pdf}%
\\[3em]%
\includegraphics[width=\linewidth]{_scripts/MC_marginal1000.pdf}%
\caption{Entropic prior}
\label{fig:MC1000}
\end{figure}
% mctests3.nb
% mcfd_6mom_unif_afssd40st0np_cok_tr_N1000_t50_L50_T0.333333333333333_s60000_a15758.0500981316
%
\begin{figure}[!p]
\centering
\includegraphics[width=\linewidth]{_scripts/MC_plot_unif1000.pdf}%
\\[3em]%
\includegraphics[width=\linewidth]{_scripts/MC_marginal_unif1000.pdf}%
\caption{Prior uniform in $\di\yF$}
\label{fig:MC1000}
\end{figure}
% mctests3.nb
% mcfd_6mom_uunif_afssd40st0np_cok_tr_N1000_t50_L0_T0.333333333333333_s60000_a15758.0500981316
%
\begin{figure}[!p]
\centering
\includegraphics[width=\linewidth]{_scripts/MC_plot_dirich1000.pdf}%
\\[3em]%
\includegraphics[width=\linewidth]{_scripts/MC_marginal_dirich1000.pdf}%
\caption{Dirichlet prior (entropic with reversed relative entropy)}
\label{fig:MC1000}
\end{figure}
% mctests3.nb
% mcfd_6mom_iunif_afssd40st0np_cok_tr_N1000_t50_L1_T0.333333333333333_s60000_a15758.0500981316
%
\begin{figure}[!p]
\centering
\includegraphics[width=\linewidth]{_scripts/MC_plot5000.pdf}%
\\[3em]%
\includegraphics[width=\linewidth]{_scripts/MC_marginal5000.pdf}%
\caption{Entropic prior}
\label{fig:MC5000}
\end{figure}
% mctests3.nb
% mcfd_6mom_unif_afssd32s_cok_tr_N5000_t180_L50_T0.333333333333333_s25800_a329212306.071189
The properties of the belief density~\eqref{eq:density_proportional} in the
case of our first data set are shown in \fig~\ref{fig:MC1000} for
$N=1\,000$ and in \fig~\ref{fig:MC5000} for $N=5\,000$. Only the first six
factorial moments were considered as our data, but it turns out that they
are informationally sufficient, leading to practically the same result as
specifying the full frequency distribution for the sample.
